---
page-layout: full

format:
  html:
    toc: true
    toc_depth: 1
    toc-location: right
    toc-expand: false
    number_sections: false
crossref:
  labels: ⓘ
  custom:
    - kind: float
      reference-prefix: Info
      key: inf
---

::: {.banner}
#
<h1 style="letter-spacing: 2.5px;">Matthew Bain</h1>

---

Data scientist, machine learning expert, lover of statistics, and
part-time musician. I build interpretable, robust, responsible machine
learning applications.
:::

::: {#inf-software style="display: none;"}
I design end-to-end data management, data analytic, and machine learning software, allowing you to harness the power of AI in your own business workflows with fine-grained control, transparency, and scalability. I use Python and R for scripting, scikit-learn and TensorFlow for machine learning, and SQL, Spark, and Google Cloud Platform to do it all at scale. 
:::

::: {#inf-apps style="display: none;"}
I design dashboards, data apps, and AI pipelines that make your data work for you and make data insights available to all. My preferred platforms are Tableau, Streamlit, Hugging Face, and Google Cloud Platform.
:::

```{r setup-r}
#| echo: false
library(reticulate)

source("src/r/cards.R")
```

```{python setup-py}
#| echo: false
import sys
import yaml
import pandas as pd

sys.path.append("src/python")
from cards import format_projects, sync_projects
```


```{python sync}
#| echo: false
#| eval: false

# 1. Synchronize records (run as needed)
sync_projects(
  src_path="~/Documents/career/resume/R/input/projects.csv",
  targ_path="data/projects.yaml",
  src_cols = [
    "link_text", "link", "tools", "short_summary"
  ],
  targ_cols=[
    "title", "name", "in_portfolio", "type",
    "img", "img_alt", "text"
  ]
)

```

```{python load}
#| echo: false

# 2. Load latest project records
with open("data/projects.yaml") as f:
  df_cards = pd.DataFrame(yaml.safe_load(f))

# 3. Format projects for cards
df_cards = format_projects(
  df=df_cards,
  default_img="icon-comp.jpg",
  default_img_alt="Photo of Mt. Fuji taken from the bullet train."
)

```

```{r process}
#| echo: false

# 4. Load cards into R
df_cards_r = pd2r(py$df_cards)

```

## Software <span class="info-icon">[-@inf-software]</span>

::: {.grid}

```{r}
#| echo: false
#| include: true
#| results: asis

print_cards(df_cards_r, keywords = c("r package"))
print_cards(df_cards_r, keywords = c("python package"))

```

:::

## Applications <span class="info-icon">[-@inf-apps]</span>

::: {.grid}

```{r}
#| echo: false
#| results: asis

print_cards(df_cards_r, keywords = c("website", "dashboard", "app", "model"))

```

:::

<!--
## Main sites

::: {.grid}

```{r}
#| echo: false
#| include: true
#| results: asis

print_cards(df_cards_r, keywords = c("blog"))

```

:::
-->

<!--
## Analyses

::: {.grid}

```{r}
#| echo: false
#| results: asis

print_cards(df_cards_r, keywords = c("analysis"))

```

:::
-->
