---
title: "writing template"
# documentclass: report
# description: 
author: "matthew bain"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  # bookdown::gitbook: default
  # bookdown::word_document2:
  # pagedown::html_paged: 
  # bookdown::pdf_document2:
  bookdown::html_document2:
    # base_format: distill::distill_article
    # base_format: bookdown::gitbook
    keep_tex: true
    toc: true
    toc_depth: 3
    toc_float: yes
    number_sections: true
    self_contained: true
    pandoc_args: ["--number-sections"] # ensure section numbering works
    # css: /Users/matthewbain/Documents/Notebook/generic-files/generic-note.css
    # css: /Users/matthewbain/Documents/Notebook/generic-files/dracula.css
    # css: generic-css.css
    theme: simplex
    highlight: pygments
    highlight_downlit: false
# header-includes: generic-header.tex
# fontsize: 11pt
# geometry: margin = 30in
# linestretch: 1
# bibliography: generic-bib.bib
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, 
                      include=TRUE, 
                      message=FALSE, 
                      warning=FALSE)
library(rgl)
library(gridExtra)

bookdown::gitbook()

setupKnitr(autoprint = TRUE)

## knitr fig defaults
# auto-save figs to current dir and add prefix/index
knitr::opts_chunk$set(fig.cap = "Figure ", fig.path = "figures/")
knitr::opts_chunk$set(dev = 'png') # set default output to svg
bookdown:::resolve_refs_html # ensure cross-referencing works?
```

\newpage

# some snippets to use/incorporate

<hr>

## some snippets

<!--# bookdown-style auto-numbered equations. -->

$$ 
\begin{align} 
  g(X_{n}) & = g(\theta) + g'({\tilde{\theta}})(X_{n} - \theta) (\#eq:res0) \\
  \sqrt{n}[g(X_{n}) - g(\theta)] 
  & = g'\left({\tilde{\theta}}\right) \sqrt{n}[X_{n} -\theta ] (\#eq:res1) \\
  & = g'\left({\tilde{\theta}}\right) \sqrt{n}[X_{n} -\theta ] (\#eq:res2)
\end{align} 
$$

$$
\begin{align}   g(X_{n}) & = g(\theta) + g'({\tilde{\theta}})(X_{n} - \theta) \notag \\  \sqrt{n}[g(X_{n}) - g(\theta)] &  = g'\left({\tilde{\theta}}\right) \sqrt{n}[X_{n} -\theta ] (\#eq:hello)\end{align}
$$

<!--# bookdown-style theorem environment -->

::: {#pyth .theorem name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse and
$a$ and $b$ denote the lengths of the other two sides, we have

$$a^2 + b^2 = c^2$$
:::

::: {.theorem name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse and
$a$ and $b$ denote the lengths of the other two sides, we have

$$a^2 + b^2 = c^2$$
:::

::: {#CZ .lemma name="CZ inequality"}
$$
\forall ~ x \in z ~\exists ~ y~  s.t. ~ ...
$$
:::

$$
\begin{align}   g(X_{n}) & = g(\theta) + g'({\tilde{\theta}})(X_{n} - \theta) \notag \\  \sqrt{n}[g(X_{n}) - g(\theta)] &  = g'\left({\tilde{\theta}}\right) \sqrt{n}[X_{n} -\theta ] (\#eq:pythagor)\end{align}
$$

<!--# the below html may configure equation environments to number (globally) by default? modify below code to replace '9' with index of current section -->

[This forum post](https://groups.google.com/g/knitr/c/OMvT03PtGPM)[^1]
contains some very useful insights on configuring RMD settings using
HTML to auto-number equations by default. More details on the [MathJax
documentation](https://docs.mathjax.org/en/latest/web/typeset.html#tex-reset)[^2]
page.

```{r q1-f1, fig.height=3.5, fig.width=5, fig.cap = 'Question (A): plot of $\\dot{x}$', eval=FALSE}
# note: no underscores in chunk labels! messes up auto-ind & cross-referencing

library(ggplot2)
library(latex2exp)
library(viridis)
library(gridExtra)

clrs = viridis(10, option = 'turbo')
# image(volcano, col = viridis(10, option = "turbo"))

# define function
func1 = rlang::as_function(~ (1 + .x^4)^4)
# func2 = rlang::as_function(~ (10 + .x^4)^4)

p1 <- ggplot() + 
  geom_function(aes(color = clrs[1*length(clrs)/4]),
                fun = func1,
                xlim = c(-2, 2)) +
  #geom_function(fun = func2,
  #              xlim = c(-2, 2),
  #              aes(color = "black")) +
  geom_hline(aes(color = 'red',
                 yintercept = -5000),
             linetype = 'dashed',
             size = .3) + 
  geom_segment(aes(x = 0, y = -5000, xend = 0.01, yend = -5000),
               arrow = arrow(length = unit(0.2, 'cm'), 
                             ends = 'last', type = 'open', 
                             angle = 40),
               color = 'red') +
  
  scale_discrete_manual(aesthetic = 'color', 
                        values = c(clrs[1*length(clrs)/4], 'red'),
                        name = '', 
                        labels = c(expression(dot(x) == (1 + x^4)^4), 
                                   'phase line')) +
  # scale_discrete_manual(aesthetic = 'linetype', 
  #                      values = c('solid', 'dashed')) + 
  # scale_colour_manual(values = c('1' = clrs[1*length(clrs)/4], 
  #                               # clrs[2*length(clrs)/4]),
  #                               '2' = 'red'))
  
  labs(x = 'x', 
       y = expression(dot(x))) + 
       # subtitle = TeX(r'($(1 + x^4)^4$)')) +
  # theme(plot.subtitle = element_text(hjust = 0.5)) + 
  theme_bw()

p1
  # theme(axis.line = element_line(arrow = arrow(angle = 30, 
  #                                              length = unit(.1,"inches"), 
  #                                              type = "open")))

  # grid.arrange(p1, p2, nrow = 1)
```

See figure \@ref(fig:q1-f1) (this is a figure cross-reference).

See equation \@ref(eq:res2)

```{r, eval=FALSE}
library(lattice)
library(plotly)

#
t <- seq(-2*pi, 2*pi, length.out = 200)
cloud(z ~ x + y, data.frame(x = 3*cos(t), y = 3*sin(t), z = t))

#
u <- seq(0, 5000, length.out = 1000)
v <- seq(0, 5000, length.out = 1000)
cloud(z ~ x + y, data.frame(x = v*cos(u), y = v*sin(u), z = v))

#
t <- seq(0, 2*pi, length.out = 50); 
u <- seq(0, 2*pi, length.out = 50); 
tu <- expand.grid(t = t, u = u)
R <- 6; 
r <- 3; 
tu <- transform(tu, 
                x = cos(t)*(R + r*cos(u)), 
                y = sin(t)*(R + r*cos(u)),
                z = r*sin(u)
)

rr<-c(-10, 10)
cloud(z ~ x + y, tu, xlim = rr, ylim = rr, zlim = rr, screen = list(y = 20));

#
xm <- outer(t, u, function(t, u) cos(t)*(R + r*cos(u)))
ym <- outer(t,u, function(t, u) sin(t)*(R + r*cos(u)))
zm <- outer(t,u, function(t, u) r*sin(u))

rr <- c(-10, 10)
wireframe(zm ~ xm + ym, xlim = rr, ylim = rr, zlim = rr, screen = list(y = 30))

#
t <- seq(-2*pi, 2*pi, length.out = 200)
dat <- data.frame(x = 3*cos(t), y = 3*sin(t), z = 2*t)

plot_ly(dat, x = ~x, y = ~y, z = ~z, type = 'scatter3d', mode = 'lines',
        line = list(width = 4))

#
dat = data.frame(x = v*cos(u), y = v*sin(u), z = v)
plot_ly(dat, x = ~x, y = ~y, z = ~z, type = 'scatter3d', mode = 'lines',
        line = list(width = 2))
```

```{r, eval=FALSE}
library(rgl)
func = rlang::as_function(~ (1 + .x^4 + .y^4)^4)

library(MASS)
# from the fitdistr example
set.seed(123)
x <- rgamma(100, shape = 5, rate = 0.1)
fit <- fitdistr(x, dgamma, list(shape = 1, rate = 0.1), lower = 0.001)
loglik <- function(shape, rate) sum(dgamma(x, shape=shape, rate=rate, 
                                           log=TRUE))
loglik <- Vectorize(loglik)
xlim <- fit$estimate[1]+4*fit$sd[1]*c(-1,1)
ylim <- fit$estimate[2]+4*fit$sd[2]*c(-1,1)

mfrow3d(1, 2, sharedMouse = TRUE)
persp3d(loglik, 
        xlim = xlim, ylim = ylim,
        n = 30)
zlim <- fit$loglik + c(-qchisq(0.99, 2)/2, 0)
next3d()
persp3d(loglik, 
        xlim = xlim, ylim = ylim, zlim = zlim,
        n = 30)
close3d()
```

# snippets section 2

## some snippets 2

::: {.theorem name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse and
$a$ and $b$ denote the lengths of the other two sides, we have

$$a^2 + b^2 = c^2$$
:::

# snippets section 3

## some snippets 3

***Assumptions**:*

-   $\gamma: (\alpha,\beta) \rightarrow \mathbb{R}^n, \bar{\gamma}: (\alpha',\beta') \rightarrow \mathbb{R}^n$

***Background***:

-   we write $\gamma \sim \bar{\gamma}$ if and only if $\bar{\gamma}$ is
    a **reparametrization** of $\gamma$

    -   i.e., if $\exists$ a **diffeomorphism**
        $\phi: (\alpha',\beta') \rightarrow (\alpha,\beta) ~ \text{such that} ~ \gamma \circ \phi = \bar{\gamma}$

## Question 1a

***Prove**: that* $\sim$ *defines an **equivalence relation** on the set
of all parametrized curves in* $\mathbb{R}^n$*.*

<hr>

*proof.*

:   *Recall.* In order for $\sim$ to be an **equivalence relation** it
    must satisfy three properties:

    1.  reflexivity: $\gamma \sim \gamma$
    2.  symmetry:
        $\gamma \sim \bar{\gamma} \iff \bar{\gamma} \sim \gamma$
    3.  transitivity:
        $\gamma \sim \bar{\gamma} ~ \text{and} ~ \bar{\gamma} \sim \bar{\bar{\gamma}} \implies \gamma \sim \bar{\bar{\gamma}}$

    Thus, to complete this proof we will check each of these properties
    in turn.

    **1) Reflexive**

    To show that $\gamma$ is a reparametrization of itself, we have to
    find a reparametrization map $\phi$ such that
    $\gamma(\phi(t)) = \bar{\gamma}(t) ~~ \text{for all} ~~ t \in (\alpha,\beta)$.

    Since in this case $\gamma = \bar{\gamma}$, let $\phi$ be the
    identity map,
    $\phi: t \in (\alpha,\beta) \rightarrow (\alpha,\beta)$ defined by
    $\phi(t) = t$, with inverse $\phi^{-1}(t) = \phi(t)$ such that
    $\phi^{-1} \circ \phi(t) = t$.

    Then,

    $$
    \gamma(\phi(t)) = \gamma(t) \text{,}
    $$

    and $\phi^{-1}(t) = \phi(t)$ is smooth, since $\phi(t)$ is
    continuously differentiable, with

    $$
    \frac{d\phi}{dt} = \dot{\phi} = 1 ~~ \text{and} ~~ \frac{d^k\phi}{dt^k} = 0 ~~ \text{for all} ~~ k > 1 \text{.}
    $$

    Thus, $\sim$ is reflexive.

    **2) Symmetric**

    *Notice*: Given $\gamma \sim \bar{\gamma}$, i.e.,
    $\gamma(\phi(t)) = \bar{\gamma}(t)$, there exists a $\phi'(t)$ such
    that $\bar{\gamma}(\phi'(t)) = \gamma(t)$ for all
    $t \in (\alpha,\beta)$.

    Namely, $\phi'(t) = \phi^{-1}(t)$ (which exists since $\phi$ is a
    diffeomorphism): $\bar{\gamma}(\phi^{-1}(t)) = \gamma(t)$.

    Thus, $\sim$ is symmetric.

    **3) Transitive**

    Let $\phi(t), \phi'(t)$ be reparametrization maps satisfying the
    following $\text{for all} ~~ t \in (\alpha,\beta)$:

    $$
    \gamma \circ \phi = \gamma(\phi(t)) = \gamma(\bar{t}) = \bar{\gamma}(t), \\
    \bar{\gamma} \circ \phi' = \bar{\gamma}(\phi'(t)) = \bar{\gamma}(\bar{t}) = \bar{\bar{\gamma}}(t).
    $$

    Then, to show that $\sim$ is transitive, we must show that there
    exists exists a $\phi''(t)$ such that

    $$
    \gamma \circ \phi'' = \gamma(\phi''(t)) = \gamma(\bar{\bar{t}}) =  \bar{\bar{\gamma}}(t) \text{.}
    $$

    *Notice:* We find $\phi''$ by composing the reparametrization maps
    $\phi'$ and $\phi$:

    Let $\phi'(\phi(t)) = \phi'(\bar{t}) = \phi''(t) = \bar{\bar{t}}$.
    Then,

    $$
    \gamma \circ \phi'' = \gamma(\phi''(t)) = \gamma(\phi'(\bar{t})) = \gamma(\bar{\bar{t}}) = \bar{\bar{\gamma}}(t) \text{.}
    $$

    By the chain rule, since $\phi, \phi'$ are smooth maps with smooth
    inverses, $\phi'' = \phi' \circ \phi$ is also smooth, with a smooth
    inverse defined by $(\phi'')^{-1} = (\phi'(\phi(t)))^{-1}$.

    Thus, $\sim$ is transitive.

    Therefore, $\sim$ is an equivalence relation

    $$
    \tag*{$\square$}
    $$

# main doc

## principles

### general

-   all dependencies imported at the top of the document with brief
    comment on their utility
-   YAML uses distill format (default overall web/article/blog layout &
    format/style - TOC, references, annotations, LaTeX + MathJax
    integration, figure/code presentation, syntax highlighting, etc.)
    and references bibtex file containing all references (books,
    manuals, articles) and LaTeX header file loading in any required
    packages for generating the desired math equations
-   use 2 header levels (sections and subsections) and place all body
    text under the subsection level - use bolded text for any 'header'
    below this level
-   bold/italicize key terms/phrases
-   all images, tables, figures come with identifiers (for within-doc
    referencing) and informative but concise (usually no more than 1-2
    lines) captions
-   all critical equations contain numerical index for easy referencing
    within document
-   parenthetical comments appear as marginal notes ('asides', in the
    language of distill), along with minor images/figures - less
    pressing comments appear as annotations
-   link to all referenced web/wiki articles (non-scientific)
-   follow standard APA referencing and reference official documentation
    for all libraries used
-   all references, annotations are listed at the foot of document and
    can be previewed by hovering the mouse over their corresponding
    in-text citations/numbers

## document setup

### default knitr options

```{r include=TRUE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

### critical libraries

```{r}
library(viridis) # generates awesome colour maps, ex:
library(highr) # applies syntax highlighting to ? *** 
library(ggplot2)
library(formatR) # expands R formatting options

clrs = viridis(10)

knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE) # enable code wrapping in code output within knitted documents? ***
```

## key ideas

### definition, theorem, remark.

<!--# T: put KIs in boxes and highlight? -->

*definition.* **Equivalence relation.**

:   An **equivalence relation** is a $\forall ~ x \in z ~ \exists$

*theorem.* **Fermat's last theorem.**

:   x

*remark.* **Properties of symmetric matrices.**

:   x

### proof

*proof.*

:   **part 1**

    *Recall.* If we ...

    $$
    \begin{align}
        3+x &=4 && \text{(solve for} \space x \text{)} (\#eq:help)\\
        x &=4-3 && \text{(subtract 3 from both sides)}\\
        x &=1   && \text{(yielding the solution.)}
    \end{align}
    $$

    We begin by

    $$
    \int_{10}^{\infty}\int_{0}^{2x + 3} 2z(4x + \sin(2z + 4)) ~ dx
    $$

    *notice*. If we make ...

    This completes the proof $\tag*{$\square\$}\$

## math[^3] [^4]

### (aligned) equations, comments, indices

*(some examples. critical mathematical objects: vectors & matrices;
functions & parametric eq'ns & vector fields; integrals & derivatives)
(T: still to add: integrals & derivatives; figure out document-wide
auto-numbering - 1,2,3,... - of equations (and suppressing on particular
lines))*

$$
\begin{align}
  3 + x & = 4 && \text{(solve for} ~ x \text{)} (\#eq:res5) \\
  x & = 4 - 3 && \text{(subtract 3 from both sides)} \\
  x & = 1   && \text{(yielding the solution)}
\end{align}
$$

$$
\begin{equation}   
  f\left(k\right) = \binom{n}{k} p^k(1 - p)^{n-k}
\end{equation}
$$

$$
\left[\begin{matrix}
  a & b \\
  c & d \\
\end{matrix}\right]
\left[\begin{matrix}
  {cx} \\ 
  y 
\end{matrix}\right] = 
\left[\begin{matrix}
  {c} \cos \left(t \right) \\ 
  \sin \left(t \right) 
\end{matrix}\right], ~ t = 0…1
$$

$$
\begin{equation}
  r = \frac{1}{n-1} \sum_{i=1}^{n} \frac{(X_i - \bar {X})(Y_i - \bar{Y})}{S_xS_y} 
\tag{by commutativity} \\    
\end{equation}
$$

### define LaTeX macros

``` {.latex}
%% define some macros (\Xbar, \sumn)
\def\Xbar{\overline{X}_\bullet}
\def\sumn{\sum_{i=1}^{n}}
```

$$
\begin{align}
\sum_{i=1}^{n}\left(X_i - \overline{X}_\bullet\right)
  & = \sum_{i=1}^{n}X_i - \sum_{i=1}^{n}\overline{X}_\bullet && \text{(comment 1)} \\
  & = \sum_{i=1}^{n}X_i - n \overline{X}_\bullet && \text{(comment 2)} (\#eq:yep) \\
  & = \sum_{i=1}^{n}X_i - \sum_{i=1}^{n}X_i (\#eq:yepyep)\\
  & = 0
\end{align} 
$$

***Some style notes***

-   add spaces: `~`

-   indentation within environments: begin each new line with two spaces

-   define macros: `\def[\define object]{ [modifiers] }`

-   new line: `\\`

-   aligned equation environment: `\begin{align} [body] \end(align}`

-   add aligned comments/equations: precede aligned text with `&`, math
    w/ `&&`

-   number equation (right align numerical index): `\tag{ [index] }`

    -   remove parentheses: insert `*` after `\tag`

-   insert math within text/tag 'sub-environment' (delimited by '`{}`':
    insert '`$ $`' around '`\`' commands

-   don't include blank lines within LaTeX environments (this leads to
    errors)

-   close out macros (`\...`) with `\;` - more generally use to close
    out compact term & add space before next

-   create bracketed term: `$\left( [term] \right)$`

-   assign label to equation `(\#eq:label)` (within equation
    environment)

### asides

<aside>

This content will appear in the gutter of the article.

</aside>

### lists {style="color: #A3EAFF"}

(*N: use tight formatting*) {style="color: \#A3EAFF"}

**numbered**

1.  number 1

2.  number 2

    <br> <!--# add break between points -->

3.  number 3

    a)  part a
    b)  part b
    c)  part c

**bulleted**

-   bullet 1
-   bullet 2
-   bullet 3

**checklist**

-   [ ] item 1

    -   [x] item 1a

-   [ ] item 2

### citations (in-text/parenthetical)

@citeR found this. [@azzalini1990look],
[link](https://bookdown.org/yihui/rmarkdown-cookbook/html-css.html).

### footnote

this is a footnote[^5]

### text formatting

This is ~~strikethrough~~, subscript~1~, superscript^2^, [small
caps,]{.smallcaps} `code`

### coloured, underlined text

Roses are \\textcolor{red}{red}, violets are \\textcolor{blue}{blue}.

### quotes

> If you never lie you never need to remember a thing.
>
> \- Mark Twain, 1857

### cross-reference (key idea/equation/visual/section)

[image reference](#river)

\@ref()

## visuals

### images

*(properly referenced w/ annotation - Google Arts & Culture CC +
artist/title/year)*

<!--# add auto-numbering -->

![a lovely
river](images/Childe%20Hassam%20-%20The%20Concord%20Meadow.jpg "scene"){#river
width="450"}

### visual asides

<aside>

```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, mpg)) + geom_point() + geom_smooth()
```

</aside>

## tables

### manually generated

*(adding col/rows, populating locally)*

| Col1  | Col2                    | Col3  |
|-------|-------------------------|-------|
| x = 2 | this is what we do here | hello |
|       |                         | y     |
|       |                         | x     |

: this is a table.

### imported & sort/searchable

<!--# truncate column widths to final character & limit at `max width` -->

```{r echo=FALSE, eval=FALSE, include=TRUE}
library(DT) # 
library(readxl)

bkshlf_path = '/Users/matthewbain/Documents/Notebook/old/bookshelf/shelf.xlsx'

bkshlf_data = read_excel(bkshlf_path, sheet = "film", range = "A10:L105")
head(bkshlf_data)

# datatable(iris)
datatable(bkshlf_data, 
          options = list(
            autoWidth = TRUE),
          fillContainer = TRUE,
          caption = htmltools::tags$caption(
            style = 'caption-side: bottom; text-align: center;', 'Table 2: ', htmltools::em('This is a simple caption for the table.')
          )) %>% 
  formatDate(columns = 'date', method = "toLocaleDateString")
```

## figures

### `ggplot` plots

```{r}
#| my-chunk, echo = FALSE, fig.width = 5,
#| fig.cap = "color palette from the viridis package. Plot displays a contour map of the Maunga Whau volcano."

library(viridis)
image(volcano, col = viridis(200))

```

```{r}
image(volcano, col = viridis(200, option = "A")) # using `magma` pallette
```

### `gganimate` animations

@gganimate

```{r eval=FALSE, include=TRUE}
library(ggplot2)
library(gganimate)
library(gapminder)

ggplot(gapminder, aes(gdpPercap, lifeExp, size = pop, colour = country)) +
  geom_point(alpha = 0.7, show.legend = FALSE) +
  scale_colour_manual(values = country_colors) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(~continent) +
  # Here comes the gganimate specific bits
  labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'life expectancy') +
  transition_time(year) +
  ease_aes('linear')
```

### `plotly` interactives

@sievert2020interactive

```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
library(rjson)
library(plotly)

url <- 'https://raw.githubusercontent.com/plotly/datasets/master/geojson-counties-fips.json'
counties <- rjson::fromJSON(file=url)
url2<- "https://raw.githubusercontent.com/plotly/datasets/master/fips-unemp-16.csv"
df <- read.csv(url2, colClasses=c(fips="character"))
fig <- plot_ly() 
fig <- fig %>% add_trace(
    type="choroplethmapbox",
    geojson=counties,
    locations=df$fips,
    z=df$unemp,
    colorscale="Viridis",
    zmin=0,
    zmax=12,
    marker=list(line=list(
      width=0),
      opacity=0.5
    )
  )
fig <- fig %>% layout(
    mapbox=list(
      style="carto-positron",
      zoom =2,
      center=list(lon= -95.71, lat=37.09))
  )
fig
```

### inline `Seaborn` figures

*(with captions, re-scaled, id for ref)*

## code

### `Python` codeblock {#python-codeblock-need-to-figure-out-how-to-output-figstats}

*(demo numpy/pandas/scipy/sklearn/keras/tensorflow)*

*(T: figure out how to output fig/stats)*

```{python, eval=FALSE}
import numpy as np

# data input
datapath = '/Users/matthewbain/Documents/Math/courses/semester II/PHYS 3G03/3G0-assignments/HW 3/code/'
csvname = datapath + 'breast_cancer_data.csv'
data1 = np.loadtxt(csvname, delimiter = ',')

# get input and output of dataset
x = data1[:-1, :]
y = data1[-1:, :]

print("hello")
```

## embedding stuff {style="red"}

### Spotify playlist

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/2JwGGcqt81VtGUT2EqZOEH?utm_source=generator" width="100%" height="380" frameBorder="0" allowfullscreen allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture">

</iframe>

### SoundCloud mix

\<iframe width="100%" height="300" scrolling="no" frameborder="no"
allow="autoplay"
src="<https://w.soundcloud.com/player/?url=https%3A//api.soundcloud.com/playlists/872489715&color=%23ff5500&auto_play=false&hide_related=false&show_comments=true&show_user=true&show_reposts=false&show_teaser=true&visual=true>"

</iframe>

::: {style="font-size: 10px; color: #cccccc;line-break: anywhere;word-break: normal;overflow: hidden;white-space: nowrap;text-overflow: ellipsis; font-family: Interstate,Lucida Grande,Lucida Sans Unicode,Lucida Sans,Garuda,Verdana,Tahoma,sans-serif;font-weight: 100;"}
<a href="https://soundcloud.com/user-752823440" title="Fujinai" target="_blank" style="color: #cccccc; text-decoration: none;">Fujinai</a>
·
<a href="https://soundcloud.com/user-752823440/sets/loops" title="Corridors" target="_blank" style="color: #cccccc; text-decoration: none;">Corridors</a>
:::

## example body text ('organization of ideas') {#basic-building-blocks-of-statements}

### Basic building blocks of statements

*(i.e., linguistic/mathematical/etc. expressions of ideas)*

1)  'first-order' statements

    -   = basic true/false statements (e.g., y is/is not --- note: can
        think of a statement like this as expressing that an object
        possesses a property or 'does something', which is roughly
        equivalent to an equivalence between object and property or
        object and operation), sometimes with categorical qualifiers
        (e.g., all, some, etc.)
    -   note: can think of these as definitions
    -   more complex definitions (e.g., of more complex
        objects/operations) may combine multiple of these using logical
        connectives (see [3])
    -   we can call these 'compound statements' of first-order
        statements

# Actionable {style="color: gray"}

-   [ ] item 1

    -   [ ] item 1b

-   [ ] item 2

# Scraps {#scraps style="color: gray"}

[^1]: forum post: <https://groups.google.com/g/knitr/c/OMvT03PtGPM>

[^2]: [MathJax doc:
    [https://docs.mathjax.org/en/latest/web/typeset.html\\\#tex-reset](https://docs.mathjax.org/en/latest/web/typeset.html\#tex-reset){.uri}](https://docs.mathjax.org/en/latest/web/typeset.html#tex-reset)

[^3]: some nice examples of LaTeX equation presentation styles in RMD:
    <https://www.math.mcgill.ca/yyang/regression/RMarkdown/example.html>

[^4]: showcases a wide variety of useful mathematical objects displayed
    in LaTeX (derivatives, limits, statistical notation, integrals,
    sequences, etc.):
    <https://rpruim.github.io/s341/S19/from-class/MathinRmd.html>

[^5]: link: <https://en.wikipedia.org/wiki/Main_Page>
